Acid-induced protein gels: from gelation to stress-induced failure

### 2015-06-04 creep_beamer.tex
Biogel, food and coauthors at the end
Reorganise completement suivant les conseils de Thomas. N'affiche plus de strain, que des strain rate Le but c'est d'expliquer pourquoi ça rescale Vire Monkman, Griffith, etc. Explique mieux le passage de 0.15 à -0.85 et dans le regime 3

\begin{frame}{Creep and yielding}
Just accepted in PRL, \textit{ArXiv 1401.8234}

\bigskip
\structure{Merciless yoghurt breakers}

\bigskip
\begin{tabu}{X[c]X[c]c}
\includegraphics[height=0.3\textheight]{Chris}&
\includegraphics[height=0.3\textheight]{Thibaut}&
\includegraphics[height=0.3\textheight]{Seb}\\
Christophe Perge & Thibaut Divoux & Sebastien Manneville\\
PhD student & CNRS researcher & Professor\\
E.N.S. Lyon &  CRPP Bordeaux & E.N.S. Lyon\\
\end{tabu}

\bigskip
\begin{description}[Special thanks]
\item[Special thanks] to Alan Parker (Firmenich) for prompting this study and providing casein \& GDL
\end{description}

\end{frame}

@@

\begin{scope}[draw]
	\node[below=0of spoon.south] (couette) {A Taylor-Couette cell where the yogurt is made \emph{in situ}};
	\draw[->] (couette) -- ($(spoon.south)+(0,2em)$);
	\node[above=0of ultrasound] {ultrasonic imaging};
	\node[above=0of webcam, text width=0.2\textwidth, align=center] {optical imaging};
	\draw[->] (spoon.north east) +(235:2em) -- (rheometer);
	\node[right=0of rheometer, text width=0.2\textwidth, align=center] {A rheometer imposes a constant stress $\sigma$ and records the strain $\gamma(t)$};
\end{scope}
\end{tikzpicture}
\end{frame}

%\tikzset{external/force remake}
\begin{frame}{The yoghurt creep experiment}
\movie[externalviewer]{\tikzsetnextfilename{creep_xp}\begin{tikzpicture}
\node[inner sep=0] (a) {\includegraphics[height=16\baselineskip]{creep_experiment.jpg}};
\node[below right=\baselineskip of a.north east, inner sep=0] (vmap) {\includegraphics[width=4\baselineskip]{jet_cmap}};

\begin{scope}[font=\footnotesize]
	\node[above=0 of vmap] {velocity map};
	\node[below=0 of vmap.south west] {-50};
	\node[below=0 of vmap.south] (v0) {0};
	\node[below=0 of vmap.south east] {50};
	\node[below=0 of v0, inner sep=0]{\si{\micro\metre\per\second}};
\end{scope}

\begin{scope}[shift={(a.north west)}, shift={(5.8\baselineskip,-1.1\baselineskip)}, ultra thick]
	\draw[Accent1, x radius=3.1\baselineskip, y radius=0.3\baselineskip] ellipse[] ++(3.1\baselineskip,0)  -- ++(0,-7.4\baselineskip)  ++(-3.1\baselineskip,0) ellipse[] ++(-3.1\baselineskip,0)  -- ++(0,7.4\baselineskip);
	\shadedraw[Accent2,ball color=Accent2, x radius=2\baselineskip, y radius=0.1\baselineskip] ellipse[] ++(2\baselineskip,0)  -- ++(0,-7.4\baselineskip)  ++(-2\baselineskip,0) ellipse[] ++(-2\baselineskip,0)  -- ++(0,7.4\baselineskip);
	\fill[Accent2, left color=black,right color=black, middle color=Accent2, ] (-0.3\baselineskip,0) rectangle +(0.6\baselineskip, \baselineskip);
	\begin{scope}[Main]
		\node[draw, minimum height=4.2\baselineskip, minimum width=1.5\baselineskip] at (2.5\baselineskip,-4\baselineskip) (window){};
		\node[draw, minimum height=7.2\baselineskip, minimum width=4\baselineskip] at (8.9\baselineskip,-4.2\baselineskip) (USV){};
		\draw(window.north east) -- (USV.north west) (window.south east) -- (USV.south west);
		\node[right, text width=4\baselineskip] at (USV.east) {ultrasound region of interest};
	\end{scope}

\draw[<->,thin] ++(-2\baselineskip,-\baselineskip) -- +(-1.1\baselineskip,0) node[midway,above] {\SI{2}{\milli\metre}};
\end{scope}
\draw[->] (window.north west) ++(-1em, 0.2em) -- +(1em,0) node[midway,above,inner sep=1pt] {$r$};
\draw[->] (window.north west) ++(-1em, 0.2em) -- +(0,-1em)  node[midway,left] {$z$};

\node[text width=4\baselineskip] at (-3\baselineskip,-2.5\baselineskip) {shear rate response};
\node at (5\baselineskip,-2.5\baselineskip) {strain response};
\end{tikzpicture}%
}{Yaourt141_enhanced.avi}
\end{frame}
%\tikzset{external/force remake=false}

\begin{frame}{Creep rheology: Three regimes}
\tikzsetnextfilename{three_regimes}
\begin{tikzpicture}
\begin{loglogaxis}[
   name=g,
	width=\textwidth,
	height=0.8\textheight,
	xmin=2e-2, xmax=4e5, xlabel={time (\si{\second})},
	ymin=0.2,ymax=2,
	ytick={0.2, 0.4,0.8,1.6}, yticklabels={0.2, 0.4,0.8,1.6},
	ylabel={strain $\gamma$},
	extra tick style={grid=major},%
	extra y ticks={1}, extra y tick labels={1.0},
	cycle list name=earthy,
	axis on top,
	]
	\fill[Accent1!20]
		(axis cs:10,0.4) ellipse[rotate=-30, x radius=0.2\textwidth, y radius=0.12\textwidth]
		(axis cs:2e2,1.6) ellipse[x radius=0.35\textwidth, y radius=0.05\textwidth]
		(axis cs:3e3,0.85) ellipse[rotate=-7.5, x radius=0.3\textwidth, y radius=0.07\textwidth]
		;
	\node[above right] at (axis cs:1e1,0.2) {primary};
	\node[below left] at (axis cs:4e5,0.7) {secondary};
	\node[left] at (axis cs:5,1.6) {tertiary};
	\addplot table{Y27_200Pa_gamma_decimated.txt} node (s200){};
	\addplot table{Y38_300Pa_gamma_decimated.txt} node (s300){};
	\addplot table{Y25_400Pa_gamma_decimated.txt}  node (s400){};
	\addplot table{Y32_550Pa_gamma_decimated.txt}  node (s550){};
	\addplot table{Y39_1000Pa_gamma_decimated.txt} node (s1000){};
\end{loglogaxis}
\begin{scope}[anchor=base, every node/.style={yshift=0.2em}]
	\node[red!40!black] at (s200 |- g.outer north) {\SI{200}{\pascal}};
	\node[red!60!black] at (s300 |- g.outer north) {300};
	\node[red!80!black] at (s400 |- g.outer north) {400};
	\node[red] at (s550 |- g.outer north) {550};
	\node[red!80!yellow] at (s1000 |- g.outer north) {1000};
\end{scope}
\end{tikzpicture}

Failure at $\gamma\approx 1$ for a well defined time $\tau_f$
\end{frame}

@@

%\tikzset{external/force remake}
\begin{frame}{Dimensionless creep response}
\begin{columns}
\column{0.55\textwidth}
\tikzsetnextfilename{primary_rescaled}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=1e-5, xmax=2, xlabel={$t/\tau_f$},
	ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
	cycle list name=earthy,
	clip mode=individual,
	]
	\addplot table[x index=1, y index=3]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[x index=1, y index=3]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[x index=1, y index=3]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[x index=1, y index=3]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[x index=1, y index=3]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[yellow, ultra thick, domain={1e-4:0.1}] {0.378*x^(-0.85)} node[Accent2,pos=0.75, below left] {$\frac{\dot{\gamma}(t)}{\dot{\gamma}_\text{min}}\sim \left(\frac{t}{\tau_f}\right)^{-0.85}$};
\end{loglogaxis}
\end{tikzpicture}

Linear viscoelasticity accounts for the Andrade exponent

\column{0.45\textwidth}
\tikzsetnextfilename{linear_rheology}
\begin{tikzpicture}
\begin{loglogaxis}[
	height=0.8\textwidth,
	width=\textwidth,
	xlabel={Frequency (\si{\hertz})}, ylabel={\textcolor{Accent1}{$G^\prime$}, \textcolor{Accent2}{$G^{\prime\prime}$}(\si{\pascal})},
	domain={6e-2:70},
	ymin=10,
	]
	\addplot[Accent1, only marks, mark=*] table{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Accent2, only marks, mark=o] table[y=LossModulus]{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Main, no marks]{100*x^0.15}  node[midway, below=1em] {$G^\prime\sim G^{\prime\prime}\sim f^{0.15}$};

\end{loglogaxis}
\end{tikzpicture}
\textcolor{Main}{
\begin{align*}
\Rightarrow & J(t) \equiv& \frac{\gamma(t)}{\sigma}\sim& t^{0.15}\\
\Rightarrow & \dot{\gamma}(t)\sim& t^{0.15-1} =& t^{-0.85}
\end{align*}
}
\end{columns}
\end{frame}

%\tikzset{external/force remake}
\begin{frame}{Tertiary creep}
\begin{columns}
\column{0.55\textwidth}
Time to failure

\tikzsetnextfilename{tertiary_rescaled}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=1e-5, xmax=2, xlabel={$(\tau_f-t)/\tau_f$},
	x dir=reverse,
	ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
	cycle list name=earthy,
	clip mode=individual,
	]
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[yellow, ultra thick, domain={1e-4:0.1}] {0.187/x} node[Accent2, pos=0.6, below right, inner sep=0] {$\frac{\dot{\gamma}(t)}{\dot{\gamma}_\text{min}}\sim \left(\frac{\tau_f}{\tau_f-t}\right)$};
\end{loglogaxis}
\end{tikzpicture}

Close to failure: 
\begin{itemize}
\item finite time singularity
\item logarithmic divergence
\end{itemize}
$\Rightarrow$ dominated by fracture growth

\column{0.45\textwidth}
\begin{block}{Fracture growth}
\includegraphics[width=0.33\textwidth]{Y110_2013-03-01_03-15-00.jpg}\hfill
\includegraphics[width=0.33\textwidth]{Y110_2013-03-01_03-20-00.jpg}\hfill
\includegraphics[width=0.33\textwidth]{Y110_2013-03-01_03-21-15.jpg}

\tikzsetnextfilename{fracture_length}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=1e-3, xmax=1, xlabel={$(\tau_f-t)/\tau_f$},
	xmode=log, x dir=reverse,
	ylabel={$\ell/H$},
	ymin=0, ymax=0.5,
	clip mode=individual,
	axis background/.style={fill=white},
	]
	\addplot[only marks, Accent1, error bars/.cd, y dir=both, y explicit] table[y error index=2]{Y110_fracturelength.txt};
	\addplot[Accent2, ultra thick, no marks, domain={1e-3:1}] {- 0.06 * ln(x)} node [pos=0.25,left=1em] {$\frac{\ell}{H}\sim \ln\frac{\tau_f-t}{\tau_f}$};
\end{axis}
\end{tikzpicture}
\end{block}
\end{columns}
\end{frame}

>>>>

@@

%Couette cell
\let\mydimb\relax
	\newlength\mydimb
	\pgfmathsetlength{\mydimb}{6\baselineskip}

\node[shape=cylinder, draw, shape border rotate=90,minimum width=\mydimb, minimum height=7\baselineskip, anchor=north, aspect=2] at (rheometer.north-|webcam.north) (Stator) {};

\node[shape=cylinder, draw, shape border rotate=90,minimum width=\mydimb-1em, minimum height=6.75\baselineskip, anchor=before bottom , aspect=1.5] at ($(Stator.before bottom)+(-0.5em,0)$) (Rotor){};

\draw[->, x radius=0.5\mydimb-2em, y radius=0.2\baselineskip]  (Stator.before top) ++(0.5\mydimb,+0.2\baselineskip) arc[start angle=90, end angle=270] node[right=1mm, font=\scriptsize] {$\sigma$};

\begin{scope}[draw]
	\node[below right=0of Stator.north east, text width=0.2\textwidth, align=center] (couette) {A Taylor-Couette cell where the yogurt is made \emph{in situ}};
	\draw[->] ($(spoon.west)+(2em,0)$) -- (Stator);
	\node[below=0of ultrasound] {ultrasonic velocimetry};
	\node[below right=0of webcam.south west, text width=0.25\textwidth, align=center] {optical imaging};
	\draw[->] (spoon.north east) +(235:2em) -- (rheometer);
	\node[right=0of rheometer, text width=0.2\textwidth, align=center] {A rheometer imposes a constant stress $\sigma$ and records the strain $\gamma(t)$};
\end{scope}
\end{tikzpicture}
\end{frame}

\begin{frame}{The yoghurt creep experiment}
\let\mylena\relax
\newlength\mylena
\pgfmathsetlength{\mylena}{0.19\textwidth}
\includegraphics[width=\mylena]{Y110_2013-03-01_02-55-11.jpg}\hfill
\includegraphics[width=\mylena]{Y110_2013-03-01_03-06-28.jpg}\hfill
\includegraphics[width=\mylena]{Y110_2013-03-01_03-19-47.jpg}\hfill
\includegraphics[width=\mylena]{Y110_2013-03-01_03-21-10.jpg}\hfill
%\includegraphics[width=\mylena]{Y110_2013-03-01_03-21-18.jpg}\hfill
\includegraphics[width=\mylena]{Y110_2013-03-01_03-21-19.jpg}\\
%\begin{center}

\bigskip\tikzsetnextfilename{creep_xp_snapshot}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=12\baselineskip,
	xmode=log,
	ymode=log,
	xlabel={$t$ (\si{\second})},
	xmin=0.1,
	ylabel={strain rate $\dot\gamma$ (\si{\per\second})}, 
	ymin=0.9e-4, ymax=2e-1,
	axis on top,
	]
 	\fill[Accent1!20]
		(axis cs:3,1e-2) ellipse[rotate=-25, x radius=0.4\textwidth, y radius=0.04\textwidth] node[below, rotate=-25, black] {power-law creep}
		(axis cs:0.8e3,2e-4) ellipse[x radius=0.05\textwidth, y radius=0.02\textwidth] node[below, black] {nucleation}
		(axis cs:1577,1e-2) ellipse[x radius=0.04\textwidth, y radius=4\baselineskip] node[below, rotate=90, black] {explosive regime}
		;
	\addplot[thick] table {Y110_300Pa.gdot}; 
	\addplot[thick, only marks, mark=o] coordinates {(687, 2.1e-4) (1476, 7.35e-4) (1509, 1.12e-3)};
	\node[below] at (rel axis cs:0.5,1) {$\sigma=\SI{300}{\pascal}$};
\end{axis}
\end{tikzpicture}
\end{frame}

\begin{frame}{Different (constant) stresses: universality}
\begin{columns}
\column{0.6\textwidth}
\tikzsetnextfilename{gdots_not_normed}%
\begin{tikzpicture}
\begin{loglogaxis}[
	name=g,
	width=\textwidth,
	height=10\baselineskip,
	xmin=2e-2, xmax=4e5, xlabel={time (\si{\second})},
	ylabel={Strain rate $\dot{\gamma}$ (\si{\per\second})},
	cycle list name=earthy,
	no marks,
	]
% 	\fill[Accent1!20]
% 		(axis cs:10,0.4) ellipse[rotate=-20, x radius=0.15\textwidth, y radius=0.02\textwidth]
% 		(axis cs:2e2,1.6) ellipse[x radius=0.35\textwidth, y radius=0.05\textwidth]
% 		(axis cs:3e3,0.85) ellipse[rotate=-7.5, x radius=0.3\textwidth, y radius=0.07\textwidth]
% 		;
	\addplot table[y index=2]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[y index=2]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[y index=2]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[y index=2]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[y index=2]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	%\addplot[Accent2, ultra thick, domain={0.1:1e3}] {0.01*x^(-0.85)} node[sloped, pos=0.75, below left] {Primary creep};

\end{loglogaxis}
\begin{scope}[anchor=base east, every node/.style={ rotate=90}]
	\node[red!40!black] at (s200 |- g.outer north) {\SI{200}{\pascal}};
	\node[red!60!black] at (s300 |- g.outer north) {300};
	\node[red!80!black] at (s400 |- g.outer north) {400};
	\node[red] at (s550 |- g.outer north) {550};
	\node[red!80!yellow] at (s1000 |- g.outer north) {1000};
\end{scope}
\end{tikzpicture}

\column{0.4\textwidth}
\structure{Normalisation}
\begin{description}[$\dot\gamma_\text{min}$]
\item[$\tau_f$] failure time 
\item[$\dot\gamma_\mathrm{min}$] minimum strain rate 
\end{description}

\smallskip
\hfill$\Rightarrow$ \colorbox{Accent1}{\color{white}\Large Physical origin?}
\end{columns}

\tikzsetnextfilename{gdots_normed}%
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=3 by 1,
			horizontal sep=3em,
			},
		width=0.35\textwidth,
		cycle list name=earthy,
		no marks,
		clip mode=individual,
		]
	\nextgroupplot[
		title={power-law creep},
		xmin=1e-5, xmax=2, xlabel={$t/\tau_f$},
		ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
		xmode=log,ymode=log,
		xtick={1e-4, 1e-2, 1},
		]
		\addplot table[x index=1, y index=3]{Y27_200Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y38_300Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y25_400Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y32_550Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y39_1000Pa_gdot_decimated.txt};
		%\addplot[yellow, ultra thick, samples at={1e-5,1e-4, 1e-3,1e-2,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9, 0.99, 0.999, 0.9999, 0.99999}] {0.378*x^(-0.85) + 0.187/(1-x)};

	\nextgroupplot[
		title={fracture nucleation},
		xmin=0, xmax=1, xlabel={$t/\tau_f$},
		ymin=0.5, ymax=4,
		restrict y to domain=0.5:10,
		]
		\addplot table[x index=1, y index=3]{Y27_200Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y38_300Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y25_400Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y32_550Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y39_1000Pa_gdot_decimated.txt};
		%\addplot[yellow, ultra thick, domain={0.01:0.99}] {0.378*x^(-0.85) + 0.187/(1-x)};

	\nextgroupplot[
		title={explosive regime},
		xmin=1e-5, xmax=2, xlabel={$(\tau_f-t)/\tau_f$},
		x dir=reverse,
		xmode=log,ymode=log,
		xtick={1e-4, 1e-2, 1},
	]
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y27_200Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y38_300Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y25_400Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y32_550Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y39_1000Pa_gdot_decimated.txt};
		%\addplot[yellow, ultra thick, samples at={1e-5,1e-4, 1e-3,1e-2,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9, 0.99, 0.999, 0.9999, 0.99999}] {0.378*(1-x)^(-0.85) + 0.187/x};
	\end{groupplot}
\end{tikzpicture}
\end{frame}

\begin{frame}{Power-law creep and plasticity}
\begin{block}{``Andrade'' creep (1910)}
\begin{itemize}
\item Power-law creep known in \alert{ductile solids} for over a century
\item Classically explained by disinclination dynamics in crystals
\item Recently explained by plastic events in glasses \textit{\footnotesize Miguel et al., PRL 2002}
\end{itemize}
\end{block}

Any plastic event in yoghurt?

\bigskip
\movie[externalviewer]{\structure{Ultrasound velocimetry}}{Yaourt110_primary.avi} $\Rightarrow$ local velocity maps
\begin{itemize}
	\item homogeneous \movie[externalviewer]{strain field}{Yaourt110_profils.avi} (no wall slip, no shear band)
	\item if present, plastic events are below our resolution (a few \si{\micro\metre})
\end{itemize}
\end{frame}

\begin{frame}{Is power-law creep damaging the structure?}
\begin{itemize}
\item Stop creep much before ($\gamma<0.3$) fracture nucleation ($\gamma\approx 1$)
\item Let relax $\Rightarrow$ No complete recovery
\item Reset deformation and start again $\Rightarrow$  superimposable
\end{itemize}

\tikzsetnextfilename{recovery}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=8\baselineskip,
	xlabel={time (\si{\hour})},
	ylabel={strain $\gamma$},
	xmin=-0.15, xmax=7.5, xtick={0, 1, ..., 7},
	axis background/.style={fill=white},
	]
	\addplot[black, no marks] table[x expr={\thisrowno{0}/3600}] {Y261_oscil_creep_recovery_100Pa_decimated.txt};
	\begin{scope}[<-,Main, inner sep=0]
	\draw (axis cs:0,0) -- +(1em,0) node[anchor=west]{$\sigma\leftarrow \SI{100}{\pascal}$};
	\draw (axis cs:1/6,0.2727007) -- +(1em,0) node[anchor=west]{$\sigma\leftarrow 0$};
	\draw (axis cs:2.388,0.0159) -- +(0,1em) node[anchor=base east]{$\gamma\leftarrow 0$};
	\end{scope}
\end{axis}
\end{tikzpicture}

\begin{itemize}
\item Undamaged structure\raisebox{-0.6\baselineskip}[0pt][0pt]{$\left.\rule{0pt}{1.\baselineskip}\right\}\Rightarrow\text{Plasticity cannot explain power law}$}
\item Viscous dissipation
\end{itemize}
\end{frame}

\begin{frame}{Power-law creep as linear response}
\begin{columns}[T]
\column{0.45\textwidth}
\tikzsetnextfilename{linear_rheology}
\begin{tikzpicture}
\begin{loglogaxis}[
	name=a,
	height=0.8\textwidth,
	width=\textwidth,
	xlabel={Frequency (\si{\hertz})}, ylabel={\textcolor{Accent1}{$G^\prime$}, \textcolor{Accent2}{$G^{\prime\prime}$}(\si{\pascal})},
	domain={6e-2:70},
	ymin=10,
	]
	\addplot[Accent1, only marks, mark=*] table{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Accent2, only marks, mark=o] table[y=LossModulus]{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Main, no marks]{100*x^0.15}  node[midway, below=1em] {$G^\prime\sim G^{\prime\prime}\sim f^{0.15}$};

\end{loglogaxis}
\end{tikzpicture}
\[ \sigma \propto  \gamma f^\alpha \xrightarrow{\mathrm{Fourier}} \sigma \propto \gamma t^{-\alpha} \]
Constant $\sigma$
\[ \gamma(t) \propto \sigma t^{\alpha} \xrightarrow{\frac{d}{dt}} \dot\gamma(t) \propto \sigma t^{\alpha-1}\]

\column{0.55\textwidth}
\tikzsetnextfilename{primary_rescaled}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=1e-5, xmax=2, xlabel={$t/\tau_f$},
	ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
	cycle list name=earthy,
	clip mode=individual,
	]
	\addplot table[x index=1, y index=3]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[x index=1, y index=3]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[x index=1, y index=3]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[x index=1, y index=3]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[x index=1, y index=3]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[yellow, ultra thick, domain={1e-4:0.1}] {0.378*x^(-0.85)} node[Accent2,pos=0.75, below left] {$\frac{\dot{\gamma}(t)}{\dot{\gamma}_\text{min}}\sim \left(\frac{t}{\tau_f}\right)^{-0.85}$};
\end{loglogaxis}
\end{tikzpicture}

Power-law creep is 
\begin{itemize}
\item the linear regime of the material 
\item up to 100\% strain!
\item explained without plasticity
\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{Explaining the explosive regime}
\begin{columns}[T]
\column{0.45\textwidth}

\includegraphics[width=0.33\textwidth]{Y110_2013-03-01_03-15-00.jpg}\hfill
\includegraphics[width=0.33\textwidth]{Y110_2013-03-01_03-20-00.jpg}\hfill
\includegraphics[width=0.33\textwidth]{Y110_2013-03-01_03-21-15.jpg}

\structure{Fracture length $\ell$}

\tikzsetnextfilename{fracture_length}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=1e-3, xmax=1, xlabel={$(\tau_f-t)/\tau_f$},
	xmode=log, x dir=reverse,
	ylabel={$\ell/H$},
	ymin=0, ymax=0.5,
	clip mode=individual,
	axis background/.style={fill=white},
	]
	\addplot[only marks, Accent1, error bars/.cd, y dir=both, y explicit] table[y error index=2]{Y110_fracturelength_log.txt};
	\addplot[Accent2, ultra thick, no marks, domain={1e-3:1}] {- 0.06 * ln(x)} node [pos=0.25,left=1em] {$\frac{\ell}{H}\sim \ln\frac{\tau_f-t}{\tau_f}$};
\end{axis}
\end{tikzpicture}

\column{0.55\textwidth}
\[ \gamma \propto \ell \propto \ln\frac{\tau_f-t}{\tau_f}\]

\[ \dot\gamma \propto \left(\frac{\tau_f-t}{\tau_f}\right)^{-1}\]

\tikzsetnextfilename{tertiary_rescaled}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=1e-5, xmax=2, xlabel={$(\tau_f-t)/\tau_f$},
	x dir=reverse,
	ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
	cycle list name=earthy,
	clip mode=individual,
	]
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[yellow, ultra thick, domain={1e-4:0.1}] {0.187/x} node[Accent2, pos=0.6, below right, inner sep=0, yshift=-0.5em] {$\frac{\dot{\gamma}(t)}{\dot{\gamma}_\text{min}}\sim \left(\frac{\tau_f}{\tau_f-t}\right)$};
\end{loglogaxis}
\end{tikzpicture}
\end{columns}
$\Rightarrow$ Explosive regime dominated by fracture growth
\end{frame}

\begin{frame}{Failure time \& master curve}
\begin{columns}[T]
\column{0.5\textwidth}
\tikzsetnextfilename{basquin}
\begin{tikzpicture}
\begin{loglogaxis}[
	width=\textwidth,
	height=0.8\textwidth,
	xlabel={$\sigma$ (\si{\pascal})},
	ylabel={$\tau_f$ (\si{\second})},
	xmin=100, ymin=10, ymax=1e6,
	xtick={100, 200,..., 1000}, xticklabels={100, 200,,, 500,,,,, 1000},
	]
	\addplot[only marks, Accent1] table[y index=3]{creep_cas4_gdl1_MCR.txt};
	\addplot[no marks, black, domain={100:1000}] {4.2e17*x^(-5.45)} node [midway, above right] {$\tau_f\sim \sigma^{-5.5}$};
	\node[above right] at (rel axis cs:0,0){No yield stress!};
\end{loglogaxis}
\end{tikzpicture}

\begin{block}{Basquin law $\tau_f\sim \sigma^{-\beta}$}
\begin{itemize}
\item fatigue (oscillatory stress)
\item heterogeneous solids
\end{itemize}
\end{block}

\column{0.5\textwidth}
\tikzsetnextfilename{secondary_rescaled}
\begin{tikzpicture}
\begin{axis}[
	width=\textwidth,
	height=0.8\textwidth,
	xmin=0, xmax=1, xlabel={$t/\tau_f$}, xtick={0,0.2,...,1},
	ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
	ymin=0.5, ymax=4,
	cycle list name=earthy,
	restrict y to domain=0.5:10,
	clip mode=individual,
	]
	\addplot table[x index=1, y index=3]{Y27_200Pa_gdot_decimated.txt} node (s200){};
	\addplot table[x index=1, y index=3]{Y38_300Pa_gdot_decimated.txt} node (s300){};
	\addplot table[x index=1, y index=3]{Y25_400Pa_gdot_decimated.txt}  node (s400){};
	\addplot table[x index=1, y index=3]{Y32_550Pa_gdot_decimated.txt}  node (s550){};
	\addplot table[x index=1, y index=3]{Y39_1000Pa_gdot_decimated.txt} node (s1000){};
	\addplot[yellow, ultra thick, domain={0.01:0.99}] {0.378*x^(-0.85) + 0.187/(1-x)};
	\draw[<-] (axis cs:0.56,1) -- +(0,1em) node[above] {$\tau_\text{min}$};
\end{axis}
\end{tikzpicture}

\structure{Master curve}
\[\frac{\dot{\gamma}(t)}{\dot{\gamma}_\text{min}} = \underbrace{\lambda \left(\frac{t}{\tau_f}\right)^{-0.85}}_\text{linear response} + \underbrace{\frac{\mu}{1 - t/\tau_f}}_\text{fractures}\]
\end{columns}
\end{frame}

@@

%\tikzset{external/force remake}

%\tikzset{external/force remake}
